### 2024-05-05 paper/sec/3_methods.tex
Update 3_methods.tex

\subsection{Feature Transform}
\indent For a given video, OpenPose outputs a directory of JSON files, with one for each frame. Before passing these outputs to a 
second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 
regardless of camera angle or relative location of the person to the camera. (Due to the nature of OpenPose outputting x, 
y values for keypoints, we have already circumvented the issue of changes in illumination.)  Our keypoint-to-angle algorithm 
aims to:
\begin{itemize}
    \item Greatly reduce the role of absolute pixel locations in identifying features
    \item Make the model invariant to differences in the user’s body structure
    \item Detect straight-line, elliptical, and hybrid motion
\end{itemize}

\indent We choose to transition away from absolute positions due to inspiration from SIFT’s usage of illumination gradients over 
absolute color values. Absolute positions could cause our model to unintentionally train on an individual's location in the 
camera view., y-positions. Similarly, we hoped to make our model invariant to the user’s height and distance from the camera 
(people in the foreground tend to appear taller than people in the background).

@@

\indent We then completed these exercises ourselves to obtain a sample 
set of testing videos. We were able to compare the instructional videos 
with the videos of ourselves following the exercises. The accuracy of 
our model was determined by comparing our test video with the Cornell 
video, and determining on our own if the numerical accuracy generated 
by the model seemed accurate. For example, a patient video following 
the instructional video perfectly should yield a 100% accuracy score, 
whereas a patient video that does not follow the instructional video 
well should yield a lower score.

>>>>

\subsection{Feature Transform}
\indent For a given video, OpenPose outputs a directory of JSON files, with one for each frame. Before passing these outputs to a 
second machine learning model, we wanted an algorithm that could map similar poses and movements to the same values, 
regardless of camera angle or relative location of the person to the camera. (Due to the nature of OpenPose outputting x, 
y values for keypoints, we have already circumvented the issue of changes in illumination.)  Our keypoint-to-angle algorithm 
aims to:
\begin{enumerate}
    \item Greatly reduce the role of absolute pixel locations in identifying features
    \item Make the model invariant to differences in the user’s body structure
    \item Detect straight-line, elliptical, and hybrid motion
\end{enumerate}

\indent We choose to transition away from absolute positions due to inspiration from SIFT’s usage of illumination gradients over 
absolute color values. Absolute positions could cause our model to unintentionally train on an individual's location in the 
camera view. Similarly, we hoped to make our model invariant to the user’s height and distance from the camera 
(people in the foreground tend to appear taller than people in the background).

@@

\indent We then completed these exercises ourselves to obtain a sample 
set of testing videos. We were able to compare the instructional videos 
with the videos of ourselves following the exercises. The accuracy of 
our model was determined by comparing our test video with the Cornell 
video, and determining on our own if the numerical accuracy generated 
by the model seemed accurate. For example, a patient video following 
the instructional video perfectly should yield a 100\% accuracy score, 
whereas a patient video that does not follow the instructional video 
well should yield a lower score.
